---
output: html_document
---
---
title: "Ex03"
author: "Hanan Jemai"
date: "October 20, 2015"
output: html_document

#1) ---Project Summary
I decided to work on a public transportation data (Currently on Uber public data set) in order to perform a data analysis for users similarities identification.
The data analysis purpose is the identification of similarities that may arise between people using public transportation system.Those similarities , once identified, would be useful for multiple uses, such as building smart classifiers for marketing campaign people targeting and/or designing intelligent transportation systems.
The analysis would probably be based on two main dimensions : Spatial and temporal.
Due to complexity , I ll start working on above stated dimensions separately.
Unless a constraint of time may be raised, a bi dimensional analysis may be part of the analysis of this project.
Actually I am using a collection of data that contains gps logs from black car pickups in San Francisco.

For a validation and generalization purpose, I am considering the application of my results on another set of data, if time allows.

#2) ---Where to buy a house in Chicago

```{r}
#Readind DB and subsettting data with crimes submitted in 2015
library(RCurl)
crimedata<-read.csv("crimedb.csv")
crime2015db<-crimedata[crimedata$Year==2015,]
crimedatalocalised<-crime2015db[!is.na(crime2015db$Longitude) & !(crime2015db$Longitude < -180 || crime2015db$Longitude > 180),]
```

```{r}
#Plotting the map
library(ggmap)
crimecoordinate<-data.frame(longitude=crimedatalocalised$Longitude,latitude=crimedatalocalised$Latitude)
map<-ggmap::get_map(location=c(min(crimecoordinate$longitude),min(crimecoordinate$latitude),max(crimecoordinate$longitude),max(crimecoordinate$latitude)),maptype="roadmap")
map<-ggmap::ggmap(map)
library(ggplot2)
map + geom_point(data = crime2015db, aes(x = Longitude, y = Latitude), color="red", size=0.6, alpha = 0.1)
```

#3) ---Univarite density of theft in 2015
```{r}
d <- density(crimecoordinate$latitude) 
plot(d,ylab = "Density",xlab = "Latitude",main = "Univariate density of thefts in 2015")
```

#4) ---3D  density function

```{r}
#Computing 2D density
library(MASS)
dens2d<-kde2d(crimecoordinate$longitude,crimecoordinate$latitude, n = 80)
#Plotting 3D density
persp(dens2d,phi = 45,xlab = "Lat",ylab = "Lon",zlab = "Density")
```

